Midwest Political Science Association

### 2023-04-18 presentations/2023-04-16_mpsa/index.qmd
Add embedded slides

---
title: "Midwest Political Science Association"
date: 2023-04-16
toc: true
abstract: |
  Annual conference of the Midwest Political Science Association (MPSA); Chicago
abstract-title: "Location"
published-title: "Presented"
page-layout: full
---

@@

Slides will be embedded here.

>>>>

---
title: "Midwest Political Science Association"
date: 2023-04-16
toc: true
abstract: |
  Annual conference of the Midwest Political Science Association (MPSA); Chicago
abstract-title: "Location"
published-title: "Presented"
image: first-slide.png
page-layout: full
---

@@

<div class="ratio ratio-16x9">
<iframe class="slide-deck" src="https://docs.google.com/presentation/d/1kCvKXx68-dG8cdpS9k6rCyNVBNMzxOU5ZwH0BaEF4Nc/embed?start=false&loop=false&delayms=3000" allowfullscreen="true" mozallowfullscreen="true" webkitallowfullscreen="true"></iframe>
</div>
